D3064R0: How to Avoid OOTA Without Really Trying

### 2024-04-04 ootavacuous.tex
Updates to Appendix E and Acknowledgements
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This test case is virtually the same as the Simple OOTA cycle
discussed in Section~\ref{sec:Simple OOTA Cycle}, the only difference
being the final values of the variables.

@@

We are grateful to David Goldblatt, Jade Alglave, and Peter
Sewell for their careful review of an early draft of this paper and
to John Wickerson for asking Paul for a rant and taking the proffered
rant seriously.
We also owe David Goldblatt a debt of gratitude for his having asked an
insightful question at the right time, his insights on combinations of
OOTA and UB, and for his ``Deathstation 9000'' demonic CPU.
% Alan Stern located many unclear statements and gaps in reasoning.
Martin Uecker contributed valuable insights on backwards-propagating UB.
Gonzalo Brito Gadeschi shared an alternative way of handling nonvolatile
atomic operations.
Richard Grisenthwaite patiently explained the architectural constraints
that prevent hardware OOTA.

>>>>

This test case is virtually the same as the Simple OOTA cycle
discussed in
Section~\ref{sec:Simple OOTA Cycle}
on
page~\pageref{sec:Simple OOTA Cycle},
the only difference being the final values of the variables.

@@

We are grateful to David Goldblatt, Jade Alglave, and Peter
Sewell for their careful review of an early draft of this paper and
to John Wickerson for asking Paul for a rant and taking the proffered
rant seriously.
We also owe David Goldblatt a debt of gratitude for his having asked an
insightful question at the right time, his insights on combinations of
OOTA and UB, and for his ``Deathstation 9000'' demonic CPU.
% Alan Stern located many unclear statements and gaps in reasoning.
Martin Uecker contributed valuable insights on backwards-propagating UB.
Gonzalo Brito Gadeschi shared an alternative way of handling nonvolatile
atomic operations.
Richard Grisenthwaite patiently explained the architectural constraints
that prevent hardware OOTA.
Mark Batty encouraged our work on new OOTA-related litmus tests.
